Emitter Source Geolocation from Imparted Rotor Blade Modulation

### 2016-10-13 Background.tex
updated references and doppler frequency calculation.

The resulting modulated signal has been used in RADAR applications. First to determine the specific characteristics of a noncooperative helicopter using time frequency analysis in (Barry D. Bullard 1991) that defines a specific signature for each parameter. The ability to detect a hovering helicopter based on the blade flashes caused by reflected RADAR pulses off the blades is defined in (J Misiurewicz 1997). The micro-doppler produced by the RADAR reflection is used in (Thayaparan, T. 2007) to determine the rotation rate of the main and tail rotor blades using the wavelet transform.

The doppler shifted signal effects the performance of common adaptive GPS anti-jamming algorithms located on a helicopter platform, unless the covariance estimation is completed within a few milliseconds. In iterative approaches the non-stationary signal characteristics cause degradation as well (F. Barbiero 2009). The affect of RBM on the BER of communications is examined in (Yaman Zhang 2000). Where effects of multi path and doppler cause large bit error rates at small elevation angles and large scattering coefficients described in their model.

The role of RBM is based on the specific doppler shift associated with where a dominant reflection occurs along the length of the of the blade, and the associated elevation angle of the transmitter. The modulated signal will then be used to create a mapping between the amount of doppler present and the distance of a transmitter on the ground.

>>>>

The resulting modulated signal has been used in RADAR applications. First to determine the specific characteristics of a noncooperative helicopter using time frequency analysis in (Barry D. Bullard 1991) that defines a specific signature for each parameter. The ability to detect a hovering helicopter based on the blade flashes caused by reflected RADAR pulses off the blades is defined in (J Misiurewicz 1997). The micro-doppler produced by the RADAR reflection is used in (Thayaparan, T. 2007) to determine the rotation rate of the main and tail rotor blades using the wavelet transform. Other types of aircraft produce modulations on a returned RADAR pulse, one type known as Jet Engine Modulation (JEM) is the product of a RADAR pulse reflecting off the jet engine blades (RADAR HANDBOOK). The information can similarly be used to quantify physical aspects of the aircraft when present in order to perform classification.

The doppler shifted signal caused by RBM effects the performance of common adaptive GPS anti-jamming algorithms located on a helicopter platform, unless the covariance estimation is completed within a few milliseconds. And in iterative based approaches the non-stationary signal characteristics cause degradation as well (F. Barbiero 2009). The affect of RBM on the BER of communications is examined in (Yaman Zhang 2000). Where effects of multi path and doppler cause large bit error rates at small elevation angles and large scattering coefficients described in the model.

The role of RBM in this thesis is based on specific doppler shifts associated with where a dominant reflection occurs along the length of the blade, and the associated elevation angle of the transmitter. The received signal is then be used to create a mapping between the amount of doppler present and the position of the transmitter on the ground.

### 2016-10-13 Radio_Propagation_Simulation.tex
updated references and doppler frequency calculation.

\section{Radio Propagation Model}
%define the math behind the physical laws that are simulated within the simulation
The propagation model defined in this project is based on the following physical phenomena, free-space path loss, reflection, and the doppler effect. They are all formally established models described in full in (Bertoni, 2000; Blaunstein, 2000; Griffiths, 1987)(FIND OTHERS). Although several effects are described within the model several were left out to simplify the computation due to the overhead of implementation in three dimensional space and because of the assumptions made about the scene model.

@@

%multipath fading
\subsection{Frequency-selective Fading}
The transmitted signal power experiences fading described by

@@

\subsection{Doppler Effect}
%define doppler effect
The Doppler effect is characterized by

>>>>

\section{Radio Propagation Model}
%define the math behind the physical laws that are simulated within the simulation
The propagation model defined in this project is based on the following physical phenomena, free-space path loss, reflection, and the doppler effect. They are all formally established models described in full in (Bertoni, 2000; Parsons, 2000; Willis, 1991)(OK). Although several effects are described within the model several were left out to simplify the computation due to the overhead of implementation in three dimensional space and because of the assumptions made about the scene model.

@@

%multipath fading
\subsection{Fading}
The transmitted signal power experiences fading described by

@@

\subsection{Doppler Effect}
%define doppler effect
The Doppler effect is characterized by (FIX Update to Bistatic Doppler)

### 2016-10-13 Ray_Tracing_Software.tex
updated references and doppler frequency calculation.

>>>>

There are several templates for simulation execution in the main.c file that are commented out to help get started, depending on the execution environment the generation of a single file can take anywhere from a few minuets to several days. Under the defaults provided a single file can be generated in approximately 15min.

### 2016-10-13 Results_new.tex
updated references and doppler frequency calculation.

Comparing the envelope difference of no pitch and pitched blade, in figures \ref{fig:azimuth_estimation_difference} and \ref{fig:diff_pitch_noCorrection} respectively, we can see that the difference calculation of the pitch is a shifted up version of the one with no pitch. Therefore we can first correct this by re-centering the pitch difference to be located around zero.

\begin{equation}
	A_{shift} = \frac{Max(EnvelopeDifference) - |Min(EnvelopeDifference)|}{2}
	\label{eqn:pitch_shift}
\end{equation}

@@

Since $\theta_{Az}$ is unknown during the calculation of this equation the correct starting phase can be determined by matching it to the $EnvelopeDifference$ with the a priori information that the cosign should be one period in length. These corrections result in the percent azimuth error of 10\% and 6.5\% elevation angle error. The error in the azimuth is quite large compared to the results when pitch is 0\textdegree but the sample is only comprised of 41 points which turns out to be 9\textdegree per sample in which 10\% error would be off by one sample. Increasing the samples per revolution would most likely decrease this error. The elevation angle percent error is within a useable range but could be decreased with further tuning to the preliminary pitch adjustment algorithm.

>>>>

Comparing the envelope difference of no pitch and pitched blade, in figures \ref{fig:azimuth_estimation_difference} and \ref{fig:diff_pitch_noCorrection} respectively, we can see that the difference calculation of the pitch is a shifted up version of the one with no pitch. Therefore we can first correct this by re-centering the pitch difference according to

\begin{equation}
	A_{shift} = \frac{Max(Max Uppe rEnvelope) - |Min(Min Lower Envelope)|}{2}
	\label{eqn:pitch_shift}
\end{equation}

where $A_{shift}$ is the amount that the difference calculation will be shifted down

@@

Since $\theta_{Az}$ is unknown during the calculation of this equation the correct starting phase can be determined by matching it to the $EnvelopeDifference$ with the a priori information that the cosign should be one period in length. These corrections result in the percent azimuth error of 0\% and 7\% elevation angle error. The elevation angle percent error is within a useable range but could be decreased with further tuning to the preliminary pitch adjustment algorithm. When the pitch corrections are applied to a transmitter elevation angle of 26.56\textdegree \space the correction achieves better performance than the unpitched calculation with percent azimuth error of 0\% and percent elevation error of 0.114\%. This is still a preliminary correction method that requires more in depth analysis but from the initial results shows merit. The increased accuracy as the elevation angle decreases relates back to figure \ref{fig:pitch_tx_elevation_angle} where as the elevation angle decreases the effect of pitch on the signal converges back to unpitched results.

### 2016-10-13 Simulation.tex
updated references and doppler frequency calculation.

>>>>

Looking back at the geometric models for transmitter azimuth angles of 0\textdegree \space, 90\textdegree \space, 180\textdegree \space, and 270\textdegree \space and their simulated counterparts shown in figure \ref{fig:verify}.

\begin{figure}
\centering
	\subfloat[0\textdegree]{
	\includegraphics[width=7cm]{images/simulation/elevation_angle_max_doppler_0deg.eps}
	}
	\subfloat[90\textdegree]{
	\includegraphics[width=7cm]{images/simulation/elevation_angle_max_doppler_90deg.eps}
	}
	\newline
	\subfloat[180\textdegree]{
	\includegraphics[width=7cm]{images/simulation/elevation_angle_max_doppler_180deg.eps}
	}
	\subfloat[270\textdegree]{
	\includegraphics[width=7cm]{images/simulation/elevation_angle_max_doppler_270deg.eps}
	}
\caption{Doppler Profile vs. Transmitter Elevation angle for various Azimuth angles.}
\label{fig:verify}
\end{figure}
